---
title: "scatterplot_20240813-20240819"
author: "Xinyi Zheng"
date: "2024-09-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I choose data from 20240813 to 20240819,
choose 4 representative college:

KINTAMPO_CENTRE_COLLEGE_MOD_PM_20240820
NTANKRO_MOD_PM_00895_20240820
WEILA_MOD_PM_01051_20240820
APESIKA_MOD_00397_20240820

# Load necessary libraries
```{r}
library(dplyr)
library(ggplot2)
library(readr)
library(tidyr)
library(tidyverse)
```

# Load and clean datasets

```{r}
ntankro_240813 <- read_csv(
  "./data/ntankro_mod_pm/DATA_20240817@FW22.csv", 
  skip = 4, 
  col_names = c("Group", "humidity", "temperature")
)[, 1:3]


ntankro_240813_clean <- ntankro_240813 %>%
  mutate(across(everything(), ~ ifelse(is.na(.), mean(., na.rm = TRUE), .)))

averaged_ntan_0813 <- ntankro_240813_clean %>%
  mutate(Group = ceiling((row_number() + 1) / 12)) %>%
  group_by(Group) %>%
  summarise(across(where(is.numeric), mean, na.rm = TRUE))

```

# plot
```{r}
ggplot(data = averaged_ntan_0813) +
  geom_point(aes(x = Group, y = humidity), color = "blue", size = 3) + 
  geom_point(aes(x = Group, y = temperature), color = "red", size = 3) +
  labs(title = "Scatterplot of Humidity and Temperature over Time",
       x = "Time",
       y = "Value") +
  theme_minimal()
```

Interpretation:
x-axis:
The time progresses from 0 minutes (start of the day) to 1440 minutes (end of the day), covering a full 24-hour period.

y-axis:
Humidity (blue line) starts high in the morning, drops around noon, and then rises again in the evening.
Temperature (red line) stays steady in the morning, increases around noon, and then drops in the evening.


```{r}
ntankro_240814 <- read_csv("./data/ntankro_mod_pm/DATA_20240817@FW22.csv", skip = 4)[, 1:3]

ntankro_240815 <- read_csv("./data/ntankro_mod_pm/DATA_20240817@FW22.csv", skip = 4)[, 1:3]

ntankro_240816 <- read_csv("./data/ntankro_mod_pm/DATA_20240817@FW22.csv", skip = 4)[, 1:3]

ntankro_240817 <- read_csv("./data/ntankro_mod_pm/DATA_20240817@FW22.csv", skip = 4)[, 1:3]

ntankro_240818 <- read_csv("./data/ntankro_mod_pm/DATA_20240817@FW22.csv", skip = 4)[, 1:3]

ntankro_240819 <- read_csv("./data/ntankro_mod_pm/DATA_20240817@FW22.csv", skip = 4)[, 1:3]
```


