---
title: "scatterplot_20240813-20240819"
author: "Xinyi Zheng"
date: "2024-09-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I choose data from 20240813 to 20240819,
choose 4 representative college:


NTANKRO_MOD_PM_00895_20240820
KINTAMPO_CENTRE_COLLEGE_MOD_PM_20240820
WEILA_MOD_PM_01051_20240820
APESIKA_MOD_00397_20240820

# Load necessary libraries
```{r}
library(dplyr)
library(ggplot2)
library(readr)
library(tidyr)
library(tidyverse)
```

# Ntankro
## Plot of temperature and humidity (one day)
```{r}
ntankro_240813 <- read_csv(
  "./data/ntankro_mod_pm/DATA_20240813@FW22.csv", 
  skip = 4, 
  col_names = c("Group", "humidity", "temperature")
)[, 1:3]


ntankro_240813_clean <- ntankro_240813 %>%
  mutate(across(everything(), ~ ifelse(is.na(.), mean(., na.rm = TRUE), .)))

averaged_ntan_0813 <- ntankro_240813_clean %>%
  mutate(Group = ceiling((row_number() + 1) / 12)) %>%
  group_by(Group) %>%
  summarise(across(where(is.numeric), mean, na.rm = TRUE))

```

```{r}
ggplot(data = averaged_ntan_0813) +
  geom_point(aes(x = Group, y = humidity), color = "blue", size = 3) + 
  geom_point(aes(x = Group, y = temperature), color = "red", size = 3) +
  labs(title = "Scatterplot of Humidity and Temperature over Time",
       x = "Time",
       y = "Value") +
  theme_minimal()
```

Interpretation:
  x-axis:
  The time progresses from 0 minutes (start of the day) to 1440 minutes (end of the day), covering a full 24-hour period.

y-axis:
  Humidity (blue line) starts high in the morning, drops around noon, and then rises again in the evening.
Temperature (red line) stays steady in the morning, increases around noon, and then drops in the evening.



# Plot of temperature and humidity (one week)
```{r}
# Function to load and clean individual datasets
load_and_clean_data <- function(file_path, date) {
  read_csv(
    file_path,
    skip = 4,
    col_names = c("Group", "humidity", "temperature")
  )[ , 1:3] %>%
    mutate(Group = as.character(Group)) %>%  # Convert Group column to character
    mutate(across(where(is.numeric), ~ ifelse(is.na(.), mean(., na.rm = TRUE), .))) %>%  # Replace NA with mean only for numeric columns
    mutate(Date = date)  # Add Date column
}

# Load all datasets with respective dates
ntankro_files <- list.files(
  "/Users/zhengxinyi/Desktop/thesis/ghana_aqi_xinyi/data/ntankro_mod_pm",
  pattern = "DATA_202408(1[3-9])@FW22.csv", 
  full.names = TRUE
)

dates1 <- seq.Date(as.Date("2024-08-13"), as.Date("2024-08-19"), by = "day")

# Apply the function to each file, adding the respective date
all_data <- mapply(load_and_clean_data, ntankro_files, dates1, SIMPLIFY = FALSE)

# Combine all datasets
ntankro_combined <- bind_rows(all_data)

# Averaging across every 12 records for each group and each day
averaged_ntan_combined <- ntankro_combined %>%
  mutate(Group = ceiling((row_number() + 1) / 12)) %>%
  group_by(Date, Group) %>%
  summarise(across(where(is.numeric), mean, na.rm = TRUE))

# Plot humidity and temperature for all days
ggplot(data = averaged_ntan_combined) +
  geom_point(aes(x = Group, y = humidity, color = Date), size = 3) +
  geom_point(aes(x = Group, y = temperature, color = Date), shape = 17, size = 3) +
  labs(title = "Scatterplot of Humidity and Temperature over Time (0813-0819)",
       x = "Time",
       y = "Value",
       color = "Date") +
  theme_minimal()
```


# Kintampo
# Plots of temperature and humidity (one week)
```{r}
# Function to load and clean individual datasets
load_and_clean_data <- function(file_path, date) {
  read_csv(
    file_path,
    skip = 4,
    col_names = c("Group", "humidity", "temperature")
  )[ , 1:3] %>%
    mutate(Group = as.character(Group)) %>% 
    mutate(across(where(is.numeric), ~ ifelse(is.na(.), mean(., na.rm = TRUE), .))) %>% 
    mutate(Date = date) 
}

# Load all datasets with respective dates
kintampo_files <- list.files(
  "/Users/zhengxinyi/Desktop/thesis/ghana_aqi_xinyi/data/kintampo_centre_college",
  pattern = "DATA_202408(1[3-9]).csv", 
  full.names = TRUE
)

dates2 <- seq.Date(as.Date("2024-08-13"), as.Date("2024-08-19"), by = "day")

# Apply the function to each file, adding the respective date
all_data <- mapply(load_and_clean_data, kintampo_files, dates2, SIMPLIFY = FALSE)

# Combine all datasets
kintampo_combined <- bind_rows(all_data)

# Averaging across every 12 records for each group and each day
averaged_kin_combined <- kintampo_combined %>%
  mutate(Group = ceiling((row_number() + 1) / 12)) %>%
  group_by(Date, Group) %>%
  summarise(across(where(is.numeric), mean, na.rm = TRUE))

# Plot humidity and temperature for all days
ggplot(data = averaged_kin_combined) +
  geom_point(aes(x = Group, y = humidity, color = Date), size = 3) +
  geom_point(aes(x = Group, y = temperature, color = Date), shape = 17, size = 3) +
  labs(title = "Scatterplot of Humidity and Temperature over Time (0813-0819)",
       x = "Time",
       y = "Value",
       color = "Date") +
  theme_minimal()
```

# Weila
# Plot of temperature and humidity (one week)
```{r}
# Function to load and clean individual datasets
load_and_clean_data <- function(file_path, date) {
  read_csv(
    file_path,
    skip = 4,
    col_names = c("Group", "humidity", "temperature")
  )[ , 1:3] %>%
    mutate(Group = as.character(Group)) %>% 
    mutate(across(where(is.numeric), ~ ifelse(is.na(.), mean(., na.rm = TRUE), .))) %>% 
    mutate(Date = date) 
}

# Load all datasets with respective dates
weila_files <- list.files(
  "/Users/zhengxinyi/Desktop/thesis/ghana_aqi_xinyi/data/weila_mod_pm",
  pattern = "DATA_202408(1[3-9]@FW22).csv", 
  full.names = TRUE
)

dates3 <- seq.Date(as.Date("2024-08-13"), as.Date("2024-08-19"), by = "day")

# Apply the function to each file, adding the respective date
all_data <- mapply(load_and_clean_data, weila_files, dates3, SIMPLIFY = FALSE)

# Combine all datasets
weila_combined <- bind_rows(all_data)

# Averaging across every 12 records for each group and each day
averaged_weila_combined <- weila_combined %>%
  mutate(Group = ceiling((row_number() + 1) / 12)) %>%
  group_by(Date, Group) %>%
  summarise(across(where(is.numeric), mean, na.rm = TRUE))

# Plot humidity and temperature for all days
ggplot(data = averaged_weila_combined) +
  geom_point(aes(x = Group, y = humidity, color = Date), size = 3) +
  geom_point(aes(x = Group, y = temperature, color = Date), shape = 17, size = 3) +
  labs(title = "Scatterplot of Humidity and Temperature over Time (0813-0819)",
       x = "Time",
       y = "Value",
       color = "Date") +
  theme_minimal()
```

# Apesika
# Plots of temparature and humidity (for one week)

```{r}
# Function to load and clean individual datasets
load_and_clean_data <- function(file_path, date) {
  read_csv(
    file_path,
    skip = 4,
    col_names = c("Group", "humidity", "temperature")
  )[ , 1:3] %>%
    mutate(Group = as.character(Group)) %>% 
    mutate(across(where(is.numeric), ~ ifelse(is.na(.), mean(., na.rm = TRUE), .))) %>% 
    mutate(Date = date) 
}

# Load all datasets with respective dates
apesika_files <- list.files(
  "/Users/zhengxinyi/Desktop/thesis/ghana_aqi_xinyi/data/apesika_mod",
  pattern = "DATA_202408(1[3-9]).csv", 
  full.names = TRUE
)

dates4 <- seq.Date(as.Date("2024-08-13"), as.Date("2024-08-19"), by = "day")

# Apply the function to each file, adding the respective date
all_data <- mapply(load_and_clean_data, apesika_files, dates4, SIMPLIFY = FALSE)

# Combine all datasets
apesika_combined <- bind_rows(all_data)

# Averaging across every 12 records for each group and each day
averaged_apesika_combined <- apesika_combined %>%
  mutate(Group = ceiling((row_number() + 1) / 12)) %>%
  group_by(Date, Group) %>%
  summarise(across(where(is.numeric), mean, na.rm = TRUE))

# Plot humidity and temperature for all days
ggplot(data = averaged_apesika_combined) +
  geom_point(aes(x = Group, y = humidity, color = Date), size = 3) +
  geom_point(aes(x = Group, y = temperature, color = Date), shape = 17, size = 3) +
  labs(title = "Scatterplot of Humidity and Temperature over Time (0813-0819)",
       x = "Time",
       y = "Value",
       color = "Date") +
  theme_minimal()
```



